### 2016-12-02 R/ITHIM.Rmd
Started working with road fatalities

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
stateVec <- c("CA","TX","NY","FL","WI","MI") #c("CA","TX","NY","FL","VA","NC","AZ")
stateVecOrdered <- c("TX","FL","NY","CA","WI","MI") #c("NC","TX","VA","FL","AZ","NY","CA")

@@

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.MI <- ITHIMList[["MI"]]
ITHIM.WI <- ITHIMList[["WI"]]

MItoCA <- data.frame(lapply(compareModels(ITHIM.MI,ITHIM.CA)$daly.delta, function(x) sum(x$M + x$F)), baseline = "MI", scenario = "CA")
WItoCA <- data.frame(lapply(compareModels(ITHIM.WI,ITHIM.CA)$daly.delta, function(x) sum(x$M + x$F)), baseline = "WI", scenario = "CA")
MItoNY <- data.frame(lapply(compareModels(ITHIM.MI,ITHIM.NY)$daly.delta, function(x) sum(x$M + x$F)), baseline = "MI", scenario = "NY")
WItoNY <- data.frame(lapply(compareModels(ITHIM.WI,ITHIM.NY)$daly.delta, function(x) sum(x$M + x$F)), baseline = "WI", scenario = "NY")

D <- melt(rbind(MItoCA,WItoCA,MItoNY,WItoNY))
names(D) <- c("baseline","scenario","disease","DALYs")

p <- ggplot(D, aes(x = disease, y = -DALYs/1e3, fill = scenario)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_y_continuous(name="DALYs Averted (thousands)") + facet_grid( . ~ baseline) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))

#+ scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + theme(axis.text.x  = element_text(angle = 270, vjust = 0.5, size = 8)) + facet_grid( . ~ disease, scales = "free_y")
```

>>>>

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
stateVec <- c("CA","TX","NY","FL","WI","MI", "OH") #c("CA","TX","NY","FL","VA","NC","AZ")
stateVecOrdered <- c("TX","FL","NY","CA","WI","MI", "OH") #c("NC","TX","VA","FL","AZ","NY","CA")

@@

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.MI <- ITHIMList[["MI"]]
ITHIM.WI <- ITHIMList[["WI"]]
ITHIM.WI <- ITHIMList[["OH"]]

prop <- 1/50
state1Vec <- c("MI","WI","OH")
state2Vec <- c("NY","CA")

foobar <- data.frame()

for( state1 in state1Vec ){
    for( state2 in state2Vec ){
        foo <- data.frame(lapply(compareModels(ITHIMList[[state1]],ITHIMList[[state2]])$daly.delta, function(x) sum(x$M + x$F)*prop), baseline = state1, scenario = state2)
        foobar <- rbind(foobar,foo)
    }
}

D <- melt(foobar)
names(D) <- c("baseline","scenario","disease","DALYs")

p <- ggplot(D, aes(x = disease, y = -DALYs/1e3, fill = scenario)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_y_continuous(name="DALYs Averted (thousands)") + facet_grid( . ~ baseline) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) + theme(legend.title=element_blank()) + scale_x_discrete(name="Disease")

#+ theme(axis.text.x  = element_text(angle = 270, vjust = 0.5, size = 8)) + facet_grid( . ~ disease, scales = "free_y")
```

## Road Fatalities

```{r roadFat}
pedDeath <- readRDS(file = "./data/BikePedDeathModelData.rds")
pedDeath <- subset(pedDeath, urbSubRur == "Urban")
pedDeath <- within(pedDeath, pedDeathLogical <- pedDeaths0913 > 0)
pedDeath <- within(pedDeath,{
  deathsTotal <- pedDeaths0913 + bikeDeaths0913
  deathsTotalLogical <- deathsTotal > 0
  activeTract <- (pctWalkToWork + pctBikeToWork ) > 0
})

D <- melt(pedDeath)

chisq.test(with(pedDeath, table(deathsTotalLogical, activeTract)))

p <- ggplot(subset(D, variable %in% c("vehMiles","pctWalkToWork","activeTract")), aes(deathsTotalLogical, value, colour = deathsTotalLogical))
p + geom_boxplot() + facet_grid(variable ~ ., scales = "free_y")
```
